Random number generation and applications on GPU’s in R?

### 2021-09-28 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.tex
changes in paper1
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@2871 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

month_GPU<-vclMatrix(month,type="integer")
result_monthgpu <- gpuRandom::fisher.sim(month_GPU, 1e6, streams=streams,
                   type="double", returnStatistics=TRUE,  Nglobal = c(128,128))
result_monthgpu$simnum
## [1] 1015808
result_monthgpu$counts
## [1] 410098
result_monthgpu$p.value
## [1] 0.4037166
\end{verbatim}
\end{kframe}
\end{knitrout}
We requested one million simulations on GPU while the actual number of simulation is 999424, and got 403274 cases whose test statitsic is below the observed threshold, so the p-value from \fct{gpuRandom::fisher.sim} for this table is about 0.40375, which is close enough to the p-value from \fct{stats::fisher.test}: 0.40380.  
\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
#using GPU
system.time(gpuRandom::fisher.sim(month_GPU, 1e6, streams=streams, 
            type="double", returnStatistics=FALSE, Nglobal = c(128,128)))
##    user  system elapsed 
##   0.699   0.005   0.703
\end{verbatim}
\end{kframe}
\end{knitrout}
\fct{gpuRandom::fisher.sim} takes about 0.32 seconds, \pkg{gpuRandom} accounts for 2.2\% of the elapsed time on CPU.

@@

week_GPU<-gpuR::vclMatrix(week,type="integer")
result_weekgpu<-gpuRandom::fisher.sim(week_GPU, 1e7, streams=streams,
                type="double",returnStatistics=TRUE,Nglobal = Nglobal)
result_weekgpu$simnum
## [1] 9994240
result_weekgpu$counts
## [1] 1223
result_weekgpu$p.value
## [1] 0.0001224705
\end{verbatim}
\end{kframe}
\end{knitrout}
With about ten million simulations, we get 1223 cases and a p-value around 0.0001224705. We summarized the results in Table \ref{tab:summary}.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
#using GPU
system.time(gpuRandom::fisher.sim(week_GPU, 1e7, streams=streams,
            type="double", returnStatistics=FALSE,Nglobal = Nglobal))
##    user  system elapsed 
##   1.899   0.000   1.898
\end{verbatim}
\end{kframe}
\end{knitrout}
\fct{stats::fisher.test} takes 90.1 seconds, while \fct{fisher.sim} takes about 1.90 seconds, the elapsed time is decreased to about 20\% of the time taken on CPU.

>>>>

month_GPU<-vclMatrix(month,type="integer")
result_monthgpu <- gpuRandom::fisher.sim(month_GPU, 1e6, streams=streams,
                   type="double", returnStatistics=TRUE,  Nglobal = c(128,128))
result_monthgpu$simNum
## NULL
result_monthgpu$counts
## [1] 403788
result_monthgpu$p.value
## [1] 0.4037628
\end{verbatim}
\end{kframe}
\end{knitrout}
We requested one million simulations on GPU while the actual number of simulation is 999424, and got 403274 cases whose test statitsic is below the observed threshold, so the p-value from \fct{gpuRandom::fisher.sim} for this table is about 0.40375, which is close enough to the p-value from \fct{stats::fisher.test}: 0.40380.  
\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
#using GPU
system.time(gpuRandom::fisher.sim(month_GPU, 1e6, streams=streams, 
            type="double", returnStatistics=FALSE, Nglobal = c(128,128)))
##    user  system elapsed 
##   0.975   0.002   1.043
\end{verbatim}
\end{kframe}
\end{knitrout}
\fct{gpuRandom::fisher.sim} takes about 0.32 seconds, \pkg{gpuRandom} accounts for 2.2\% of the elapsed time on CPU.

@@

week_GPU<-gpuR::vclMatrix(week,type="integer")
result_weekgpu<-gpuRandom::fisher.sim(week_GPU, 1e7, streams=streams,
                type="double",returnStatistics=TRUE,Nglobal = Nglobal)
result_weekgpu$simNum
## NULL
result_weekgpu$counts
## [1] 1224
result_weekgpu$p.value
## [1] 0.0001225
\end{verbatim}
\end{kframe}
\end{knitrout}
With about ten million simulations, we get 1223 cases and a p-value around 0.0001224705. We summarized the results in Table \ref{tab:summary}.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
#using GPU
system.time(gpuRandom::fisher.sim(week_GPU, 1e7, streams=streams,
            type="double", returnStatistics=FALSE,Nglobal = Nglobal))
##    user  system elapsed 
##   1.899   0.000   1.898
\end{verbatim}
\end{kframe}
\end{knitrout}
\fct{stats::fisher.test} takes 90.1 seconds, while \fct{fisher.sim} takes about 1.90 seconds, the elapsed time is decreased to about 20\% of the time taken on CPU.
